---
title: "R Notebook"
output: html_notebook
---


---

# Save Final Data  {.appendix}  

saved data after analysis to `gallbladderFC.xlsx`.

```{r save final data}
saveRDS(gallbladderFC, "gallbladderFC.rds")

writexl::write_xlsx(gallbladderFC, "gallbladderFC.xlsx")

file.info("gallbladderFC.xlsx")$ctime

```



\pagebreak


# Libraries Used {.appendix}  

```{r citation}
citation()
```


```{r library citations}
citation("tidyverse")
citation("readxl")
citation("janitor")
citation("report")
citation("finalfit")
# citation("ggstatplot")
```


```{r library citation as report, results='asis'}
report::cite_packages(session = sessionInfo())
```



The jamovi project (2019). jamovi. (Version 0.9) [Computer Software]. Retrieved from https://www.jamovi.org.
R Core Team (2018). R: A Language and envionment for statistical computing. [Computer software]. Retrieved from https://cran.r-project.org/.
Fox, J., & Weisberg, S. (2018). car: Companion to Applied Regression. [R package]. Retrieved from https://cran.r-project.org/package=car.





```{r session info}
sessionInfo()
```



\pagebreak



# Notes {.appendix}  

Last update on `r Sys.time()`  

Serdar Balci, MD, Pathologist  
drserdarbalci@gmail.com  
https://rpubs.com/sbalci/CV   

